INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION

### 2016-09-13 paper.tex
Add model illustration

>>>>

\subsection{Adversarial Cost Types}

%TODO: explain -log(\hat{y}) and log(1 - \hat{y})

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{model.pdf}
    \caption{The model consists of three neural networks. The encoder $E$ produces
    the intermediate representation $h$ which used in the recognizer $R$ and 
    in the discriminator $D$. The hidden representation $h$ is trained to improve
    the recognition and minimize the discrimination accuracy. The discriminator
    is a classifier trained to maximize its accuracy on the gender or the noise type
    recognition task.}
    \label{fig:model}
\end{figure}
